Measuring dimension

### 2012-08-30 Dimension/src/dimension.tex
...

As noted by Stanley, this is only a simplistic view and the study of the dimension of a dataset can also give vital clues to scaling behaviors and critical phenomena in the process from which the data originated. Thus the theorist can not only validate his work by the dimension, but also use it as a guide. When we investigate the notion of dimension more closely we must give up intuitive notion and the only thing we can say is that the gemotry of a set or space produces various power laws related to scaling and that these power laws will usually have the same exponent in common. There is a common intuition in the natural sciences that power law phenomena with the same exponent will likely share some similarity in their underlying components. Thus the dimension can be an important guide in finding the universal principles common to  complex phenomana.

@@

\[
p(d = r | d \leq r_{\max}) = D_t \frac{r^{D_t-1}}{{r_{\max}}^D_t} = D_t \frac{1}{r} \left (\frac{r}{r_{\max}} \right ) ^ {D_t} 
\]

>>>>

For this reason, any scientist who deals with fractal phenomena will want to measure dimension, in order to capture those phenomena in meaningful statistics. Examples are biologists studying the emergence of structure, geologists studying the fractal surfaces and outlines of land masses and rock formations or physicists studying the measures of strange attractors.

@@

\[
p(d = r | d \leq r_{\max}) = D_t \frac{r^{D_t-1}}{{r_{\max}}^{D_t}} = D_t \frac{1}{r} \left (\frac{r}{r_{\max}} \right ) ^ {D_t} 
\]
